Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-06-28 paper/revision/responseToReviewers.tex

\item \emph{Only two applications are considered in the literature review, bioacoustics and urban sound environment, but they allow to present a problem that also exists in other application areas.}

$\rightarrow$ ML

\item \emph{The authors present their technique as opposed to the BOF approach, that is considered "state of the art". BOF maybe a popular technique but the fact that gets rid of the temporal structure makes it useless in many tasks. In fact, in DCASE 2013 BOF was the chosen baseline system but no participant proposed that technique. Certainly, BOF allows the authors to make stronger the point about describing an acoustic scene from a few distinct events, but perhaps they should avoid to claim BOF as "the" state of the art in this problem.}

$\rightarrow$
As discussed above in the response to the first reviewer, the application in the DCASE 2013 paper, classification, is different from the one proposed in our work, similarity retrieval. For classification, the BOF approach is indeed not the state of the art. However, in acoustic scene similarity retrieval, we are not aware of any systems which outperform the BOF. As such, it is indeed the state of the art for the similarity retrieval task. The manuscript has been revised to clarify this point.

### 2018-06-28 paper/lostanlenRelevanceScattering.tex
Address relation to BOF and state of the art
More analysis of results in Figure 3

A closely related field is that of urban sound environment analysis.
In this context, a popular approach is the bag of frames (BOF), first applied to the problem by Aucouturier et al. \cite{aucouturier2007bag}.
It models an auditory scene using high-level summary statistics computed from local features, typically implemented by Gaussian mixture models (GMMs) of MFCCs.
Recently, this representation was shown to perform comparably to direct averaging of the features for a variety of tasks \cite{lagrange:hal-01082501}.
This contrasts with the typical morphology of acoustic scenes, a ``skeleton of events on a bed of textures,'' where a few discrete sound events are superimposed upon a stationary acoustic background \cite{nelken2013}.
Such events are not well-characterised by summarizing short-term features, but are better described by large-scale temporal evolution of auditory scenes.
The latter approach should therefore prove more fruitful in measuring auditory scene similarity.

@@

As seen in Figure \ref{fig:ASS_-1}, the BOF approach behaves similarly to the early approach when applied both to the MFCCs and the scattering features.

>>>>

A closely related field is that of urban sound environment analysis.
In this context, a popular approach is the bag of frames (BOF), first applied to the problem by Aucouturier et al. \cite{aucouturier2007bag}.
It models an auditory scene using high-level summary statistics computed from local features, typically implemented by Gaussian mixture models (GMMs) of MFCCs.
While BOF has largely been superseded by more sophisticated methods for the task of acoustic scene classification \cite{7100934}, it remains the best-performing model for acoustic scene similarity retrieval.
Recently, this representation was shown to perform comparably to direct averaging of the features for a variety of tasks \cite{lagrange:hal-01082501}.
This contrasts with the typical morphology of acoustic scenes, a ``skeleton of events on a bed of textures,'' where a few discrete sound events are superimposed upon a stationary acoustic background \cite{nelken2013}.
Such events are not well-characterised by summarizing short-term features, but are better described by large-scale temporal evolution of auditory scenes.
The latter approach should therefore prove more fruitful in measuring auditory scene similarity.

@@

As seen in Figure \ref{fig:ASS_-1}, scattering features significantly outperform the baseline MFCCs for both BOF and early integration schemes.
This is expected, as the scattering transform extends the MFCCs by including supplementary amplitude modulation information \cite{Anden2014}.
We also note that applying PCA reduction to the scattering transform has little effect for the early integration scheme.
In the context of summary statistics, $30$ dimensions are sufficient to discriminate between auditory scenes.

Comparing the BOF to early integration, both approaches perform similarly for MFCCs and PCA-reduced scattering features alike.
This is in line with previous results on BOF \cite{lagrange:hal-01082501}, where it is found to perform similarly as similarity retrieval on features averaged over the entire recording.
